Exploring C-MMHP

### 2020-06-22 output_scripts/mod_cmmhp.Rmd
further work on the c-mmhp

---
title: "Exploring C-MMHP"
author: "Owen Ward"
output:
  html_document:
    toc: yes
    df_print: paged
    toc_float: yes
    code_folding: hide
---

@@

@@

$$
q_1^{i,j} = \exp(-\eta_3 f_i)\hspace{1cm}   \ q_{0}^{i,j} = \exp(-\eta_3 f_j),
$$
and the limiting proportion of 
time spent in the active state is $logistic(\eta_3 (f_i-f_j))$.

@@

```{r, contour_alpha}
f_alpha <- function(f_i,f_j,eta_1,eta_2) {
  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j))
}
plot_alpha <- function(f_alpha, grid_size = 0.1,eta_1 = 1,eta_2 = 1) {
  plt <- tibble(x = seq(0,1,by = grid_size),y = seq(0,1,by = grid_size)) %>%
    expand(x,y) %>%
    mutate(value = map2_dbl(x,y,f_alpha,eta_1,eta_2)) %>%
    ggplot(aes(y,x)) + geom_contour_filled(aes(z = value))  +
    scale_x_reverse()+ 
    xlab("f_j (Receive)") + ylab("f_i (Send)") + geom_abline(slope = -1, intercept = 0,
                                                             col = "red")
  print(plt)
}

@@

We want this to take larger values when $f_i>f_j$ than when $f_i < f_j$ although it is 
hard to claim it is not symmetric currently.

>>>>

---
title: "Exploring C-MMHP"
author: "Owen Ward"
output:
  html_document:
    toc: yes
    df_print: paged
    toc_float: yes
    code_folding: hide
    number_sections: true
---

@@

This does not appear to indicate any clear relationship between these degree
corrected estimates for the out/in baseline rates and the expert
ranking.

@@

$$
q_1^{i,j} = \exp(-\eta_3 f_i)\hspace{1cm}   \ q_{0}^{i,j} = \exp(-\eta_3 f_j),
$$
and the limiting proportion of 
time spent in the active state is $logistic(\eta_3 (f_i-f_j))$,
i.e

$$
\frac{q_{0}^{i,j}}{q_{0}^{i,j}+q_1^{i,j}}  \equiv \frac{\exp(-\eta_3 f_j)}{\exp(-\eta_3 f_j)+\exp(-\eta_3 f_i)}.
$$

@@

```{r, contour_alpha}
f_alpha <- function(f_i,f_j,eta_1,eta_2) {
  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j))
}
plot_alpha <- function(fun = f_alpha, grid_size = 0.1,eta_1 = 1,eta_2 = 1, ...) {
  plt <- tibble(x = seq(0,1,by = grid_size),y = seq(0,1,by = grid_size)) %>%
    expand(x,y) %>%
    mutate(value = map2_dbl(x,y,fun,eta_1,eta_2,...)) %>%
    ggplot(aes(y,x)) + geom_contour_filled(aes(z = value))  +
    scale_x_reverse()+ 
    xlab("f_j (Receive)") + ylab("f_i (Send)") + geom_abline(slope = -1, intercept = 0,
                                                             col = "red")
  print(plt)
}

@@

We want this to take larger values when $f_i>f_j$ than when $f_i < f_j$ although it is 
hard to claim it is not symmetric currently. This could be due to using a different
plot function than originally used by Jing.

## Incorporate the latent state

We can also plot $\alpha Z(t)$, which will capture the overall structure
which will be seen.

```{r}

latent_state <- function(f_i,f_j,eta_3) {
  exp(-eta_3*f_j)/(exp(-eta_3*f_j) + exp(-eta_3*f_i)  )
}

f_alpha_z <- function(f_i,f_j,eta_1,eta_2,eta_3) {
  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j)) * latent_state(f_i,f_j,eta_3)
}

plot_alpha(fun = f_alpha_z,eta_1 = 3, eta_2 = 1,grid_size = 0.01,eta_3 = 4)

This much more clearly captures the upper triangular structure we wish to have.

## With modified latent state

We can repeat this with the second proposed modification above, which seemed 
to capture the dynamics well.

```{r}

latent_state_2 <- function(f_i,f_j,eta_3) {
  f_i*exp(-eta_3*f_j)/(f_i*exp(-eta_3*f_j) + f_j*exp(-eta_3*f_i)  )
}

f_alpha_z <- function(f_i,f_j,eta_1,eta_2,eta_3) {
  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j)) * latent_state_2(f_i,f_j,eta_3)
}

plot_alpha(fun = f_alpha_z,eta_1 = 3, eta_2 = 1,grid_size = 0.01,eta_3 = 4)

This is almost identical to the previous plot, with perhaps a slight shift when
both $f_i$ and $f_j$ are large.
